Re-finding to support a Deep Web Question Answering System

### 2010-03-05 paper/semsearch10/content/results_futurework_conclusion.tex
tried to address changes for results section

Researchers have stated 39, 57, and 63 percent of web queries are unique \cite{1277770,331405,621942}.  We believe that an even higher number of those are parameterizable, meaning, a set of queries are all related and may be answered using a single QRM.  It is difficult to discover this property.  Previous work suggest techniques to find related queries but it will take a new method to discover parameterizable queries.

>>>>

%% I may have misstated the statistics that are unique/repeats
% need to clarify the statistics 
%% Add language about how we 
Researchers have stated 39, 57, and 63 percent of web queries are unique \cite{1277770,331405,621942}.  We believe that a large percentage of the stated unique queries are in-fact related and parameterizable, meaning, several subsets of unique queries may be all related and may be answered using a single QRM.  It is difficult to discover this property between queries.  Previous work suggest techniques to find related queries but it will take new efficient methods to discover parameterizable queries.
